Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-06 paper/presentation.tex
More to presentation

% Datoen blir også trykket på forsida. 
\date{X. December 2010}
%\date{} % Bruk denne hvis du ikke vil ha noe dato på forsida.

@@

\begin{frame}
  \frametitle{Python-bindings}
  \begin{itemize}
  \item Optimized version of candidates available at eBACS: ECRYPT Benchmarking
  of Cryptographic Systems.
  \item We have used the fastest, capable C-version available for our target
  architecture, 32-bit.
  \item Made them available in Python by the use of Cython in ``SHA3Lib''
  \end{itemize}
\end{frame}

>>>>

% Datoen blir også trykket på forsida. 
\date{December 7th 2010}
%\date{} % Bruk denne hvis du ikke vil ha noe dato på forsida.

@@

\begin{frame}
  \frametitle{Python-bindings}
  \begin{itemize}
  \item Optimized version of candidates available at eBACS: ECRYPT Benchmarking
  of Cryptographic Systems. (SUPERCOP toolkit)
  \item We have used the fastest, capable C-implementations available for our target
  architecture, 32-bit.
  \item Made them available in Python by the use of Cython in ``SHA3Lib''
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Modification of Tahoe-LAFS}
  \begin{enumerate}
  \item Quick hack to quickly swap used hash implementation
  \item Benchmarking data (number of hashoperations, timers)
  \end{enumerate}
\end{frame}

\begin{frame}
    \frametitle{Tahoe-LAFS is SLOW}
    \begin{itemize}
        \item On 1 Gbit network - with modern computers
        \item Tahoe-LAFS output is about 10-12 Megabyte/s
        \item SCP output is about 80 Megabyte/s
        \item High-CPU load on client but not on storage nodes
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Benchmarking}

    INSERT graphs.. % TODO
\end{frame}

\begin{frame}
    \frametitle{Criticism}
    \begin{itemize}
        \item SUPERCOP is a good idea, however we see problems
            \begin{enumerate}
                \item Speed of Update() is neglected
                \item Implementations are not correct according to specification
                \item Some implementations fails to fullfill the basic requirements
                of HASH functions
            \end{enumerate}
        \item Our implementations are not the fastest possible
            \begin{enumerate}
                \item Some performance loss by using Cython (?)
                \item Not (always) the fastest versions from SUPERCOP
            \end{enumerate}
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Remaining}
    \begin{enumerate}
        \item Figure out inconsistencies.
        \item Finish report....
    \end{enumerate}
\end{frame}

\begin{frame}
    \frametitle{Conclusion}
    \begin{enumerate}
        \item There is a performance gain by switching to another hash
        function
        \item However, the gain is small and we believe improving other areas
        could imporve performance more
    \end{enumerate}
\end{frame}
